TUDataset: A collection of benchmark datasets for learning with graphs

### 2020-05-10 main.tex
Fixed GNN evaluation.

eintragen
IMDB-BINARY GINWithJK 72.93333333333334 0.5185449728701322 4.122566622330749
IMDB-BINARY GIN 72.06666666666668 0.3091206165165233 4.024370206076419
IMDB-MULTI GINWithJK 50.644444444444446 1.01153837126587 4.59462917806765
IMDB-MULTI GIN 48.84444444444444 0.37051848890073463 3.523185988018918
NCI1 GINWithJK 79.67558799675588 0.4130683399269047 1.5714739782362184
NCI1 GIN 78.01297648012977 0.38333502994634977 1.9142541830162463
PROTEINS GINWithJK 71.27895752895752 0.9574183044143284 4.459876910576175
PROTEINS GIN 71.16527241527241 0.3211668436757545 3.612551907408368
REDDIT-BINARY GINWithJK 90.31666666666668 0.4326918328582383 1.9894862541760765

REDDIT-BINARY GIN 90.18333333333334 0.39228674319799567 2.169805418823438

>>>>

Bitte eintragen
IMDB-BINARY GINWithJK 72.93333333333334 0.5185449728701322 4.122566622330749
IMDB-BINARY GIN 72.06666666666668 0.3091206165165233 4.024370206076419
IMDB-MULTI GINWithJK 50.644444444444446 1.01153837126587 4.59462917806765
IMDB-MULTI GIN 48.84444444444444 0.37051848890073463 3.523185988018918
NCI1 GINWithJK 79.67558799675588 0.4130683399269047 1.5714739782362184
NCI1 GIN 78.01297648012977 0.38333502994634977 1.9142541830162463
PROTEINS GINWithJK 71.27895752895752 0.9574183044143284 4.459876910576175
PROTEINS GIN 71.16527241527241 0.3211668436757545 3.612551907408368
REDDIT-BINARY GINWithJK 90.31666666666668 0.4326918328582383 1.9894862541760765
REDDIT-BINARY GIN 90.18333333333334 0.39228674319799567 2.169805418823438
